Worflow

### 2017-06-11 R/workflow.Rmd
clean up some comments

```{r}
res <- computeDevianceResiduals(zinb, core)
res[1:3,1:3]
```

@@

Let's add the normalized values as an assay dataset in our SummarizedExperiment object.

```{r}
assays(se)[['normalizedValues']] <- res
```

@@

```{r}
W <- getW(zinb50)
d <- dist(W)
fit <- cmdscale(d, eig = TRUE, k = 2)
plot(fit$points, col = col_clus[as.character(clus.labels)], main = 'MDS', pch = 20,
     xlab = 'Component 1', ylab = 'Component 2')
legend(x = 'bottomright', legend = unique(names(col_clus)), cex = .5,
       fill = unique(col_clus), title = 'Sample')
```

Let's add W to the colData of our SummarizedExperiment object.

```{r}
W <- data.frame(W)
colnames(W) <- paste0('W', 1:ncol(W))
colData(se) <- cbind(colData(se), W)
```

FP: what do you think of implemented a "compute_normalized_values" argument to zinbFit for summarizedExperiment objects where zinbFit would take as input a SummarizedExperiment object and return a summarizedExperiment object with slots added for normalized values and W?

@@

FP: What about the following call to RSEC?

@@

```{r rsec_50}
W <- colData(se)[, grepl('^W', colnames(colData(se)))]
W <- as.matrix(W)
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  #symbol for samples missing from original clustering
	metadata$clusterLabels[is.na(metadata$clusterLabels)]<- -2 
  seObj<-SummarizedExperiment(t(W),colData=metadata)
  print(system.time(ceObj <- RSEC(seObj, k0s = 4:15, alphas = c(0.1),
                                  betas = 0.8,
                clusterFunction = "hierarchical01", minSizes=1,
                ncores = NCORES, isCount=FALSE,
                subsampleArgs = list(resamp.num=100,
                                     clusterFunction="kmeans",
                                     clusterArgs=list(nstart=10)),
                seqArgs = list(k.min=3, top.can=5), verbose=TRUE,
                combineProportion = 0.7,
                mergeMethod = "none")))
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

@@

FP: Not sure we should show the following heatmap using the W, we should rather use the normalized values (following heatmap).

EP: Agreed

```{r heatmap, eval=FALSE}
plotHeatmap(ceObj, clusterSamplesData = "dendrogramValue", 
            breaks = .99)
```

>>>>

```{r}
res <- assays(zinb)[['normalizedValues']]
res[1:3,1:3]
```

@@

@@

```{r}
W <- colData(se)[, grepl('^W', colnames(colData(se)))]
W <- as.matrix(W)
d <- dist(W)
fit <- cmdscale(d, eig = TRUE, k = 2)
plot(fit$points, col = col_clus[as.character(clus.labels)], main = 'MDS', pch = 20,
     xlab = 'Component 1', ylab = 'Component 2')
legend(x = 'bottomright', legend = unique(names(col_clus)), cex = .5,
       fill = unique(col_clus), title = 'Sample')
```

@@

@@

```{r rsec_50}
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  #symbol for samples missing from original clustering
	metadata$clusterLabels[is.na(metadata$clusterLabels)]<- -2 
  seObj<-SummarizedExperiment(t(W),colData=metadata)
  print(system.time(ceObj <- RSEC(seObj, k0s = 4:15, alphas = c(0.1),
                                  betas = 0.8,
                clusterFunction = "hierarchical01", minSizes=1,
                ncores = NCORES, isCount=FALSE,
                subsampleArgs = list(resamp.num=100,
                                     clusterFunction="kmeans",
                                     clusterArgs=list(nstart=10)),
                seqArgs = list(k.min=3, top.can=5), verbose=TRUE,
                combineProportion = 0.7,
                mergeMethod = "none")))
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

@@
